# caret package

**The caret Package**^[https://topepo.github.io/caret/]

>The caret package (short for Classification And REgression Training) is a set of functions that attempt to streamline the process for creating predictive models. The package contains tools for:
>
>* data splitting
* pre-processing
* feature selection
* model tuning using resampling
* variable importance estimation  

## 전처리

```{r}
if(!require(caret)) {
  install.packages("caret")
  library(caret)
}

if(!require(dplyr)) {
  install.packages("dplyr")
  library(dplyr)
}

if(!require(palmerpenguins)) {
  install.packages("palmerpenguins")
  library(palmerpenguins)
}

```

### Creating Dummy Variables

```{r}
str(penguins)
```

더미변수는 model.matrix() 함수와 dummyVars() 함수를 통해 변환할 수 있다.  

```{r}
model.matrix(species ~ ., penguins) %>% head
```


```{r}
dummies <- dummyVars(species ~ ., data = penguins)
predict(dummies, penguins) %>% head
```

### Zero- and Near Zero-Variance Predictors

```{r}
nearZeroVar(penguins, saveMetrics = T)
```

```{r}
data(mdrr)
nzv <- nearZeroVar(mdrrDescr, saveMetrics = T); nzv[nzv$nzv,][1:10,]
```

```{r}
nzv <- nearZeroVar(mdrrDescr)
filteredDescr <- mdrrDescr[, -nzv]
```

### Identifying Correlated Predictors



### Linear Dependencies

### The preProcess Function

### Centering and Scaling

### Imputation

### Transforming Predictors

### Putting It All Together

### Class Distance Calculations





## 데이터 분할

## 모델 학습

## 병렬처리 및 하이퍼 파라메터

## Recipes

## 성능평가

