# caret package

**The caret Package**^[https://topepo.github.io/caret/]

>The caret package (short for Classification And REgression Training) is a set of functions that attempt to streamline the process for creating predictive models. The package contains tools for:
>
>* data splitting
* pre-processing
* feature selection
* model tuning using resampling
* variable importance estimation  

## 전처리

```{r}
if(!require(caret)) {
  install.packages("caret")
  library(caret)
}

if(!require(dplyr)) {
  install.packages("dplyr")
  library(dplyr)
}

if(!require(palmerpenguins)) {
  install.packages("palmerpenguins")
  library(palmerpenguins)
}

```

### Creating Dummy Variables

```{r}
str(penguins)
```

더미변수는 model.matrix() 함수와 dummyVars() 함수를 통해 변환할 수 있다.  

```{r}
model.matrix(species ~ ., penguins) %>% head
```


```{r}
dummies <- dummyVars(species ~ ., data = penguins)
predict(dummies, penguins) %>% head
```

### Zero- and Near Zero-Variance Predictors

```{r}
nearZeroVar(penguins, saveMetrics = T)
```

```{r}
data(mdrr)
nzv <- nearZeroVar(mdrrDescr, saveMetrics = T); nzv[nzv$nzv,][1:10,]
```

```{r}
nzv <- nearZeroVar(mdrrDescr)
filteredDescr <- mdrrDescr[, -nzv]
```

### Identifying Correlated Predictors

```{r}
descrCor <- cor(filteredDescr)
highCorr <- sum(abs(descrCor[upper.tri(descrCor)]) > .999)
```

```{r}
summary(descrCor[upper.tri(descrCor)])
```

```{r}
highlyCorDescr <- findCorrelation(descrCor, cutoff = .75)
filteredDescr <- filteredDescr[,-highlyCorDescr]
descrCor2 <- cor(filteredDescr)
summary(descrCor2[upper.tri(descrCor2)])
```

### Linear Dependencies

```{r}
ltfrDesign <- matrix(0, nrow=6, ncol=6)
ltfrDesign[,1] <- c(1, 1, 1, 1, 1, 1)
ltfrDesign[,2] <- c(1, 1, 1, 0, 0, 0)
ltfrDesign[,3] <- c(0, 0, 0, 1, 1, 1)
ltfrDesign[,4] <- c(1, 0, 0, 1, 0, 0)
ltfrDesign[,5] <- c(0, 1, 0, 0, 1, 0)
ltfrDesign[,6] <- c(0, 0, 1, 0, 0, 1)
```

```{r}
comboInfo <- findLinearCombos(ltfrDesign); comboInfo
```

```{r}
ltfrDesign[, -comboInfo$remove]
```

### The preProcess Function

데이터 전처리 함수, `train()` 함수 수행 시 데이터와 I/F를 제공한다.


### Centering and Scaling

```{r}
set.seed(96)
inTrain <- sample(seq(along=mdrrClass), length(mdrrClass)/2)
training <- filteredDescr[inTrain,]
test <- filteredDescr[-inTrain,]
trainMDRR <- mdrrClass[inTrain]
testMDRR <- mdrrClass[-inTrain]

preProcValues <- preProcess(training, method = c("center", "scale"))

trainTransformed <- predict(preProcValues, training)
testTransformed <- predict(preProcValues, test)
```


### Imputation

### Transforming Predictors

### Putting It All Together

```{r}
if(!require(AppliedPredictiveModeling)) {
  install.packages("AppliedPredictiveModeling")
  library(AppliedPredictiveModeling)
}
data("schedulingData")
str(schedulingData)
```

```{r}
pp_hpc <- preProcess(schedulingData[, -8],
                     method = c("center", "scale", "YeoJohnson")); pp_hpc;
```

```{r}
transformed <- predict(pp_hpc, schedulingData[, -8])
head(transformed)
```
```{r}
mean(schedulingData$NumPending == 0)
```

```{r}
pp_no_nzv <- preProcess(schedulingData[, -8],
                        method = c("center", "scale", "YeoJohnson", "nzv")); pp_no_nzv
pp_no_nzv$method
```

```{r}
predict(pp_no_nzv, newdata = schedulingData[1:6, -8])
```

### Class Distance Calculations

## 데이터 분할



## 모델 학습

## 병렬처리 및 하이퍼 파라메터

## Recipes

## 성능평가

